%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Trey Hunner (http://www.treyhunner.com/)
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Shaila Ang} % Your name
\address{0450 540 118 \\ shailadaneang@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf University of Sydney} \hfill {\em 2013-2019} \\ 
Bachelor of Health Science and Masters of Nursing \\
Business Management \smallskip \\
Student Representative (2013 - 2014) - Health Science and Nursing  \\
Exchange Student at Aiesec Sydney \\
Overall GPA: Distinction (3.5/4.0)

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{Westpac - BT Financials}{November 2018 - Present}{Business Analyst}{Barangaroo, Sydney}
\item I was responsible for writing user stories for ROA Template, testing user stories, gathering and analysing data. I also created a wireframe for a feature that will be added on BT Panorama and designed a landing page for both investors and advisers. Aside from my responsibilities as a Business Analyst, I also led a team of interns in making a strategy to understand and resolve the problem underlying the BT Panorama.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Vita Group}{August - October 2018}{Sales Consultant}{Penrith, NSW}
\item My responsibility was to provide a personalised service and advice to uncover customers' needs and provide them with solutions
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Telstra}{January - July 2018}{Sales Consultant}{Market St. Sydney}
\item My responsibility is to share my knowledge about the products and services  offered by Telstra. 
\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Tiffany and Co.}{October 2017 - January 2018}{Sales Consultant}{Bondi Junction, Bondi}
\item My responsibility was to provide the Tiffany Blue experience to customers, assist customers in finding the styles that would suit them and resolve their queries in empathetic manner.

\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Royal North Shore Hospital}{2015-2016}{Assistant Nurse}{St Leonards}
\item My responsibility was to assist the nurses in attending the needs of the patients. 

\end{rSubsection}
\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Wireframe & Microsoft Powerpoint \\
Creating a prototype & Invision\\
Visual Design & Paint 3D, Adobe Photoshop, Canva \\
Machine Learning &  Python with Numpy and Pandas \\
Website (coded) &  HTML5 and CSS \\
Data Visualisation & Tableau\\
Typesetting Document & Latex\\
Programming & Java and Java Script, Python, HTML and CSS\\

\end{tabular}

\end{rSection}


%----------------------------------------------------------------------------------------
%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

%	Volunteering Activities and Projects
%----------------------------------------------------------------------------------------
\begin{rSection}{Volunteering Activities}

\begin{rSubsection}{CoderDojo}{2018-Present}{Champion}{Microsoft Store Sydney and Parramatta}
\item I was responsible for mentoring young people with programming. I facilitate their learning activity by demonstrating the content to cover and assisting them in developing their own small projects or chosen activity. I am also for marketing and liaising with stakeholders who are interested in partnering with CoderDojo.   

\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Sydney University}{2013-2014}{Student Representative}{Campberdown,NSW}
\item I gathered information from students and communicate their views to the faculty members. I did this to improve the learning experience of current and future students.

\end{rSubsection}
%------------------------------------------------

\begin{rSubsection}{Aiesec Poland}{November 2013- February 2014}{Intern}{Poznan, Poland}
\item I taught English to Polish Kindergartens and assisted the organisation in promoting Global Host Family and diversity to Polish students. 

\end{rSubsection}

\end{rSection}

%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Awards and Recognitions}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Techfugees Hackathon (2018) &  Our team (Elevate) won Second Place. \\
Sydney University & Advertised Bursary (2018),NSW Health Grant (2017), Robert Maple Brown (2013)\\
Macquarie University (2013) & Overall Excellence in Science\\
\end{tabular}

\end{rSection}

%\begin{rSection}{Section Name}

%Section content\ldots

%\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
